Improved Cation Binding to Lipid Bilayer with Negatively Charged POPS by Effective Inclusion of Electronic Polarization

### 2019-10-18 Manuscript/manuscript.tex
Merging text by Pavel to the methods

Electronic continuum correction (ECC) is an implicit mean-field representation of 
the electronic polarization in classical MD simulations, 
which has been recently applied to improve empirical models for ions and
 biomolecules containing charged groups such as proteins and lipids. 
\cite{melcr18, Pluharova2014, martinek17, duboue2018insulin, Mason2019, Duboue2018MgZn}
For simple ions in water, the electronic polarizability
can be taken into account by scaling the charge with a constant factor 
%\begin{equation}
 \mbox{$ f_q = \frac{1}{\sqrt{\epsilon_{el}}} \approx 0.75$,}
%\end{equation}
where  $\epsilon_{el} = 1.78$ is the high-frequency dielectric constant of electrons in water \cite{leontyev09}.
In addition to the charge, the Lennard-Jones parameter~$\sigma$ of the ions needed to be modified 
to improve the description of hydration properties of ions with respect to scattering data in these studies 
by scaling with a factor $ 0.72 < f_\sigma \leq 1$.
The reason for the small readjustment of the ionic radii is that the original force fields were often developed such that the first peak on the experimental ion-water oxygen radial distribution function was reproduced. 
Upon charge scaling this peak typically moved to slightly larger distances and the agreement with experiment was then restored by a small decrease of the Lennard-Jones~$\sigma$ parameter.
More details about ECC are contained in references \citenum{melcr18, martinek17, leontyev09, leontyev11, leontyev14}.

>>>>

%Electronic continuum correction (ECC) is an implicit mean-field representation of 
%the electronic polarization in classical MD simulations, 
%which has been recently applied to improve empirical models for ions and
% biomolecules containing charged groups such as proteins and lipids. 
%\cite{melcr18, Pluharova2014, martinek17, duboue2018insulin, Mason2019, Duboue2018MgZn}
%For simple ions in water, the electronic polarizability
%can be taken into account by scaling the charge with a constant factor 
%%\begin{equation}
% \mbox{$ f_q = \frac{1}{\sqrt{\epsilon_{el}}} \approx 0.75$,}
%%\end{equation}
%where  $\epsilon_{el} = 1.78$ is the high-frequency dielectric constant of electrons in water \cite{leontyev09}.

Electrostatic interactions between charges in a dielectric medium are attenuated by a factor equal to the
corresponding relative permittivity (dielectric constant). Standard non-polarizable force fields are capable to
account for the dielectric response from the orientation of molecules (low-frequency), but fail to account for the electronic (high frequency) polarization.
In most biologically relevant environments this high frequency dielectric constant is ~2 (for water the value is 1.78).
This means that for a non-polarizable force field that would strictly account only for the low-frequency dielectric response
interactions between charges in aqueous environments should be further attenuated by a factor of 1.78, which is mathematically
equivalent by scaling the charges by a factor of ~0.75 \cite{leontyev09,leontyev14}. 
This electronic continuum correction (ECC), which can be view as a mean-field continuum way for accounting for electronic polarization,
has been shown to significantly improve the description of interactions between aqueous ions and biologically relevant charged groups \cite{pluharova13,kohagen14,kohagen14b,melcr18,xie16,kroutil17,bruce18}
%[dx.doi.org/10.1021/jp402532e, dx.doi.org/10.1021/jp5005693, dx.doi.org/10.1021/jz502099g, DOI: 10.1021/acs.jpcb.7b12510, https://doi.org/10.1021/acs.jpcb.5b10755, DOI:10.1007/s00894-017-3490-x, https://doi.org/10.1063/1.5017101].
This correction is particularly important for high charge density species where it helps to remove artifacts such as excessive ion pairing in water [dx.doi.org/10.1021/jp402532e, dx.doi.org/10.1021/jp310719g]. One should, however, bear in mind that existing non-polarizable force fields have been parameterized also using experimental data, which means that they may to a certain extent include implicitly electronic polarization effects. Therefore, in such cases a charge scaling factor between 0.75 and 1 should carefully be adjusted such that electronic polarization effect are not overaccounted for.

In addition to the charge, the Lennard-Jones parameter~$\sigma$ of the ions needed to be modified 
to improve the description of hydration properties of ions with respect to scattering data in these studies 
by scaling with a factor $ 0.72 < f_\sigma \leq 1$.
The reason for the small readjustment of the ionic radii is that the original force fields were often developed such that the first peak on the experimental ion-water oxygen radial distribution function was reproduced. 
Upon charge scaling this peak typically moved to slightly larger distances and the agreement with experiment was then restored by a small decrease of the Lennard-Jones~$\sigma$ parameter.
More details about ECC are contained in references \citenum{melcr18, martinek17, leontyev09, leontyev11, leontyev14}.
